---
output: github_document
---

<!--  README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width=6, 
  fig.height=4
)
```

The First-order Integer-valued Autoregressive (INAR(1)) model with 
zero-inflated (ZI-INAR(1)) and hurdle (H-INAR(1)) innovations is widely 
used in studying integer-valued time-series data, such as crime count and 
heatwave frequency. This work implemented the INAR(1) models in Stan.

## Installation

You can install ZIHINAR1 from GitHub with:

```r
remotes::install_github("fushengyy/ZIHINAR1")
```

\[Available Soon\] Or you can install the released version of
HeckmanStan from [CRAN](https://CRAN.R-project.org) with:

```r
install.packages("ZIHINAR1")
```

## Basic Features get_stanfit()

The package contains main function named get_stanfit().

```r
stan_fit <- get_stanfit(mod_type, distri, y, n_pred = 4,
                        thin = 2, chains = 1, iter = 2000, warmup = iter/2,
                        seed = NA)
```

- mod_type: Character string indicating the model type.
  Use "zi" for zero-inflated models and "h" for hurdle models.

- distri: Character string specifying the distribution.
  Options are "poi" for Poisson or "nb" for Negative Binomial.

- y: A numeric vector of integers representing the observed data.

- n_pred: Integer specifying the number of time points for future predictions
  (default is 4).

- thin: Integer indicating the thinning interval for Stan sampling 
  (default is 2).

- chains: Integer specifying the number of Markov chains to run (default is 1).

- iter: Integer specifying the total number of iterations per chain
  (default is 2000).

- warmup: Integer specifying the number of warmup iterations per chain
  (default is iter/2).

- seed: Numeric seed for reproducibility (default is NA).

## Example

The following are examples showing how to fit the INAR(1) model when data 
is generated from a zero-inflated Negative Binomial (ZINB) distribution.

```{r example1, out.width = '70%',  fig.align = "center", message=FALSE, warning=FALSE}
library(ZIHINAR1)
y_data <- data_simu(n = 100, alpha = 0.5, rho = 0.3, theta = c(5, 2), 
                    mod_type = "zi", distri = "nb")
stan_fit <- get_stanfit(mod_type = "zi", distri = "nb", y = y_data, n_pred = 5, 
                        iter = 2000, chains = 1, warmup = 500, 
                        thin = 2, seed = 42)
get_est(distri = "nb", stan_fit = stan_fit)
get_mod_sel(y = y_data, mod_type = "zi", distri = "nb", stan_fit = stan_fit)
get_pred(stan_fit = stan_fit)
```
